COG-ED Manuscript

### 2021-10-12 06_Paper/COG-ED/Manuscript.Rmd
Update Corinna manuscript & analyses

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(bibtex)
```

@@

  library(here)         # to set a directory without defined paths, "here" package
  library(tidyverse)    # plotting and managing data, "tidyverse" package
  library(bayestestR)   # computing area under the curve, "bayestestR" package
  library(papaja)       # APA conform output, "papaja" package

@@

  # put relevant data into a dataframes

@@

  # the target column will contain 1 for targets and 0 for all non-targets
  data_nback[data_nback == "Target"] <- 1
  data_nback[data_nback == "Pretarget"|data_nback == "Lure"|data_nback == "Distractor"] <- 0
  data_nback$target <- as.numeric(data_nback$target)
  # the response column will contain 1 for responses and 0 for all non-responses
  data_nback[data_nback == "left"|data_nback == "right"] <- 1
  data_nback[data_nback == "None"] <- 0
  data_nback$response <- as.numeric(data_nback$response)
  # the choice column will contain 1 for the left button and 2 for the right button
  data_ED[data_ED == "EDleftbutton"] <- 1
  data_ED[data_ED == "EDrightbutton"] <- 2
  data_ED$choice <- as.numeric(data_ED$choice)

  # since only the last choice of each comparison is relevant, we will keep only those rows

  data_ED <- data_ED[data_ED$step == 6,]
  data_ED <- subset(data_ED, select = -c(step))

@@

We used *R Studio* [@RCT2020; @RStudioTeam2020] with the main packages *tidyverse* [@Wickham2019] and *basetestR* [@Makowski2019] for all our analyses.
The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at github.com/ChScheffel/CERED.

## Questionnaires
To assess perceived task load, we used the NASA Task Load Index (NTLX) [@Hart1988], a 6-item questionnaire with the dimensions mental load, physical load, effort, frustration, performance, and time pressure.
Need for Cognition was assessed using the 16-item short form of the Need for Cognition Scale [@Bless1994; @Cacioppo1984].
Several other personality questionnaires were used in this study but are the topic of the registered report for the second lab session regarding ED in emotion regulation tasks and will not be analyzed here.
A full list of questionnaires and measures can be found in Appendix 1.

@@

  # apply the addition or subtraction of 0.015625 to the last choices

@@

  # z-transform the hit rate and the false alarm rate

@@

      hypothesis1a_anova <- summary(aov(h1a_data$d ~ h1a_data$level))
      hypothesis1a_posthoc <- TukeyHSD(aov(h1a_data$d ~ h1a_data$level))
      remove(h1a_data)

@@

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# FIXME I propose to put the packages required here at the very beginning.
library(bibtex)
```

@@

  library(here)         # to set a directory without defined paths, "here" package
  library(tidyverse)    # plotting and managing data, "tidyverse" package
  library(bayestestR)   # computing area under the curve, "bayestestR" package
  library(papaja)       # APA conform output, "papaja" package
  library(nlme)         # fitting nonlinear mixed-effects model
# we could add the package versions here additionally

@@

  # put relevant data into data frames

@@

  # the target column will contain 1 for targets and 0 for all non-targets
  data_nback[data_nback == "Target"] <- 1
  data_nback[data_nback == "Pretarget"|data_nback == "Lure"|data_nback == "Distractor"] <- 0
  data_nback$target <- as.numeric(data_nback$target)
  # the response column will contain 1 for responses and 0 for all non-responses
  data_nback[data_nback == "left"|data_nback == "right"] <- 1
  data_nback[data_nback == "None"] <- 0
  data_nback$response <- as.numeric(data_nback$response)

  # the choice column will contain 1 for the left button and 2 for the right button
  data_ED[data_ED == "EDleftbutton"] <- 1
  data_ED[data_ED == "EDrightbutton"] <- 2
  data_ED$choice <- as.numeric(data_ED$choice)

  # since only the last choice of each comparison is relevant, we will keep only those rows
  data_ED <- data_ED[data_ED$step == 6,]
  data_ED <- subset(data_ED, select = -c(step))

@@

We used *R Studio* [@RCT2020; @RStudioTeam2020] with the main packages *tidyverse* [@Wickham2019] and *basetestR* [@Makowski2019] for all our analyses.
# FIXME add version no. and packages
The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at github.com/ChScheffel/CERED.

## Questionnaires
To assess perceived task load, we used the NASA Task Load Index (NTLX) [@Hart1988], a 6-item questionnaire with the dimensions mental load, physical load, effort, frustration, performance, and time pressure.
FIXME: NTLX seems not to be the commonly used abbreviation. We my refer to NASA TLX / NASA-TLX or just TLX. We may provide more information (see Strobel et al. 2020):
In the NASA-TLX, participants evaluate their subjective perception of the mental, physical and temporal svs of a particular task, as well as their performance, effort and frustration during the task on a 20-point scale for each dimension. In its original, the NASA-TLX also requires comparisons of two dimensions each. For this study, we relinquished the comparison due to time restrictions.

Need for Cognition was assessed using the 16-item short form of the Need for Cognition Scale [@Bless1994; @Cacioppo1984].
FIXME: We may need to add information on example items, rating scale and reliability (see diffpp):
_Need for Cognition_ was assessed with the 16-item short version of the German NFC scale [@Bless1994]. Responses to each item (e.g., "Thinking is not my idea of fun", recoded) were recorded on a 7-point Likert scale ranging from -3 (completely disagree) to +3 (completely agree). The scale shows comparably high internal consistency [Cronbach’s $\alpha$ > .80; @Bless1994; @Fleischhauer2010].

Several other personality questionnaires were used in this study but are the topic of the registered report for the second lab session regarding ED in emotion regulation tasks and will not be analyzed here.
A full list of questionnaires and measures can be found in Appendix 1.

@@

  # apply the addition or subtraction of 0.015625 to the last choices
# FIXME why do we have to do this?

@@

  # z-transform the hit rate and the false alarm rate
  # FIXME: What makes this transformation necessary? Why per n-back level separately? Is this the standard procedure?
  # FIXME: for z-transformation we could use function scale:

  # # create new variables
  # dprime$falsealarmrate.z = dprime$hitrate.z =NA
  # for (i in 1:4) {
  #    dprime$hitrate.z[which(dprime$level == i)]        <- scale(dprime$hitrate[which(dprime$level == i)])
  #    dprime$falsealarmrate.z[which(dprime$level == i)] <- scale(dprime$falsealarmrate[which(dprime$level == i)])
  # }

@@

      hypothesis1a_anova <- summary(aov(h1a_data$d ~ h1a_data$level))
      hypothesis1a_posthoc <- TukeyHSD(aov(h1a_data$d ~ h1a_data$level))
      # TODO  check for posthoc test alternative
      #       anova calculation
      remove(h1a_data)

@@

# FIXME what about RT preprocessing
  # correct / postcorrect     *see Westbrook et al. 2013, table 1: correct trials
  # log-transformation
  # valid answers: false alarm vs. missing -> plausible responses

@@

# define variables -------------------------------------------------------------
# dependent variable:     SV                    numeric                 data_SV
# indepenendent variable: n-back level [1-4]    numeric                       
# controlled regressors:  d'                    numeric                 dprime
#                         mRT                   numeric                 rt

# get all relevant variables ---------------------------------------------------

h2b_data <- cbind(data_SV, dprime["d"], rt["meanrt"])

# check and specify correct data types -----------------------------------------
str(h2b_data)

# center predictors ------------------------------------------------------------
# center level 1 predictors
# two ways: centering at the grand mean (CGM) vs. centering within cluster (CWC) = group mean centering
# level 1 predictor (SV) is of substantive interest
# > CWC

# d'
h2b_data$d.mwc <- ave(h2b_data$d, h2b_data$subject, FUN = function(x) mean(x, na.rm = T))
h2b_data$d.cwc <- h2b_data$d - h2b_data$d.mwc

# mRT
h2b_data$meanrt.mwc <- ave(h2b_data$meanrt, h2b_data$subject, FUN = function(x) mean(x, na.rm = T))
h2b_data$meanrt.cwc <- h2b_data$meanrt - h2b_data$meanrt.mwc

# level
h2b_data$level.mwc <- ave(h2b_data$level, h2b_data$subject, FUN = function(x) mean(x, na.rm = T))
h2b_data$level.cwc <- h2b_data$level - h2b_data$level.mwc

# no level 2 predictors

# change global coding to orthogonal sum-to-zero contrast by -------------------
options(contrasts = c("contr.sum", "contr.poly"))

# null model -------------------------------------------------------------------
# m0_h2b <- nlme(model = sv ~ 1,
#                data = h2b_data,
#                random = ~ 1 | subject, 
#                method = "REML")

# full model -------------------------------------------------------------------
# random intercept vs. random slope ???
# "subject-specific intercepts" speaks for random-slopes-model, as within this model 
# the slope is allowed to vary between subjects

# m1_h2b <- nlme(sv ~ d.cwc + meanrt.cwc + level.cwc + (level.cwc| subject),
#                data = h2b_data,
#                fixed = ...,
#                random = ...,
#                control = ...,
#                method = "REML")

# initVals <- getInitial(sv ~ d.cwc + meanrt.cwc + level.cwc, data = h2b_data)

# get initial values for mlm start
fm.lm <- lm(sv ~ d.cwc + meanrt.cwc + level.cwc, h2b_data)
st <- coef(fm.lm)

m1_h2b <- nlme(sv ~ d.cwc + meanrt.cwc + level.cwc,
               data = h2b_data,
               #fixed = d.cwc + meanrt.cwc + level.cwc ~ 1,
               fixed = list(d.cwc ~ 1, meanrt ~ 1, level.cwc ~ 1),
               random = level.cwc ~ 1 | subject,
               start = list(fixed = st[2:4]),
               method = "REML")

# change global coding to default ----------------------------------------------
options(contrasts = c("contr.treatment", "contr.poly"))
